---
# Reproducible Research: Peer Assessment 1



## Loading and preprocessing the data
```{r}
library(dplyr)
library(ggplot2)
library(knitr)
df_na<-read.csv("activity.csv")
df<-subset(df_na,!(is.na(steps)))
```

## What is mean total number of steps taken per day?
```{r}
a<-tbl_df(df)
a<-group_by(a,date,.drop=FALSE)
a<-summarize(a,total=sum(steps))
qplot(a$total,binwidth=1000)+xlab("Steps")
mean(a$total)
median(a$total)
```


## What is the average daily activity pattern?
```{r}
b<-tbl_df(df)
b<-group_by(b,interval,.drop=FALSE)
b<-summarize(b,avg=mean(steps))
ggplot(b,aes(interval,avg))+geom_line()+ggtitle("Average daily activity")+xlab("Interval")+ylab("Steps")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
b[which.max(b$avg),][[1]]
```

## Imputing missing values
```{r}
sum(is.na(df_na))
c<-tbl_df(df)
new<-df_na
c<-group_by(c,interval,.drop=FALSE)
c<-summarize(c,avg=mean(steps))
c<-as.data.frame(c)
filler<-function(interval,steps){
	value<-NA
	if(is.na(steps))
	value<-c$avg[c$interval==interval]
	else
	value<-steps
	return(value)
	}
new$steps<-mapply(filler,new$interval,new$steps)
filled_in<-new
c<-new
c<-group_by(c,date,.drop=FALSE)
c<-summarize(c,total=sum(steps))
qplot(c$total,binwidth=1000)+xlab("Steps")
mean(c$total)
median(c$total)
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
filled_in$date<-as.Date(filled_in$date)
weekd<-c("Monday","Tuesday","Wednesday","Thursday","Friday")
filled_in$days<-factor((weekdays(filled_in$date) %in% weekd),levels=c(FALSE,TRUE),labels=c('weekend','weekday'))
d<-filled_in
d<-group_by(d,interval,days)
d<-summarise(d,avg=mean(steps))
ggplot(d,aes(x=interval,y=avg))+geom_line()+facet_grid(days~.)
```
